Cache is King: Presenting a Suite of Fast, Correlation Function Codes

### 2015-02-25 paper/ms.tex
Epic re-write of the io.c file. Can read in arbitrary numbers of fields of DOUBLE precision
Added some protection for C++ compilers. Switched the objects files to the front for the Makefiles

\usepackage{amsmath}
\usepackage{aas_macros}
\usepackage{rotating}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}
\usepackage{listings}
\usepackage{caption}
\usepackage{url}
\journal{Astronomy and Computing}

%%% Definitions added by Manodeep 
\newcommand{\Msun}{M_{\odot}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\sdss}{{\small{SDSS}}\xspace}
\newcommand{\hMpc}{\ensuremath{{h^{-1}Mpc}\xspace}}
\newcommand{\hkpc}{\ensuremath{{h^{-1}kpc}\xspace}}
\newcommand{\emcee}{\texttt emcee}
\newcommand{\rmax}{\ensuremath{{r_{max}}}\xspace}
\newcommand{\xir}{\ensuremath{{\xi(r)}}\xspace}
\newcommand{\wprp}{\ensuremath{{w_p(r_p)}}\xspace}
\newcommand{\xirppi}{\ensuremath{{\xi(r_p,\pi)}}\xspace}
\newcommand{\todo}[1]{\marginpar{TODO}{\color{red}#1}}

@@

\subsection{Partitioning the Particles based on \rmax}

\begin{figure}[htbp]
\centering
\includegraphics[clip=true]{tikz_grid}
\caption{A 2-D grid showing the bin-lattice partitioning scheme. The bigger square show the entire 
domain, the red circles show a random distribution of 100 particles. Let's say we want to compute all pairs 
for the target blue point, then we would only have to consider red points that are within one cell (the dark shaded region). 
A circle with radius \rmax is also drawn to shown the actual pairs that will eventually count in the correlation function.} 
\end{figure}

@@

>>>>

\usepackage{amsmath}
\usepackage{aas_macros}
\usepackage{rotating}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}
\usepackage{listings}
\usepackage{caption}
\usepackage{url}
\usepackage{adjustbox}
\journal{Astronomy and Computing}

%%% Definitions added by Manodeep 
\newcommand{\Msun}{M_{\odot}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\sdss}{{\small{SDSS}}\xspace}
\newcommand{\hMpc}{\ensuremath{{h^{-1}Mpc}\xspace}}
\newcommand{\hkpc}{\ensuremath{{h^{-1}kpc}\xspace}}
\newcommand{\emcee}{\texttt emcee}
\newcommand{\rmax}{\ensuremath{{r_{max}}}\xspace}
\newcommand{\xir}{\ensuremath{{DD(r)}}\xspace}
\newcommand{\xiofr}{\ensuremath{{\xi(r)}}\xspace}
\newcommand{\wprp}{\ensuremath{{w_p(r_p)}}\xspace}
\newcommand{\xirppi}{\ensuremath{{\xi(r_p,\pi)}}\xspace}
\newcommand{\todo}[1]{\marginpar{TODO}{\color{red}#1}}

@@

\subsection{Partitioning the Particles based on \rmax}
Fig.~\ref{fig:grid} shows a schematic 2-D grid that corresponds to our partitioning scheme.
\begin{figure}[htbp]
\centering
\includegraphics[clip=true]{tikz_grid}
\caption{A 2-D grid showing the bin-lattice partitioning scheme. The bigger square show the entire 
domain, the red circles show a random distribution of 100 particles. Let's say we want to compute all pairs 
for the target blue point, then we would only have to consider red points that are within one cell (the dark shaded region). 
A circle with radius \rmax is also drawn to shown the actual pairs that will eventually count in the correlation function.} 
\label{fig:grid}
\end{figure}

@@

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}
up to $\sim$ 10 threads.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{ccccc} 
\toprule
\multirow{2}{*}{\textbf{Nthreads}}   &
\multicolumn{4}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{1.0em}r{1.0em}){2-5}
&
\multicolumn{1}{c}{$\boldsymbol{\xir}$}    &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$} &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}   & 
\multicolumn{1}{c}{$\boldsymbol{\xiofr}$}   \\
\midrule
\input{timings_Mr19_openmp} 
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}
